The Cost of Transportation : Spatial Analysis of US Fuel Prices

### 2017-02-25 Docs/Paper/paper.tex
gecocoding_ok

@@

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{Author name}

@@

@@

@@

@@

\bibliographystyle{elsarticle-harv}
\bibliography{}
%

>>>>

%%%%%%%%%%

%%%%%
% variable to include comments or not in the compilation ; set to 1 to include
\def \draft {1}
%\def \draft {0}

% writing utilities

% comments and responses
%  -> use this comment to ask questions on what other wrote/answer questions with optional arguments (up to 4 answers)
\usepackage{xparse}
\usepackage{ifthen}
\DeclareDocumentCommand{\comment}{m o o o o}
{\ifthenelse{\draft=1}{
    \textcolor{red}{\textbf{C : }#1}
    \IfValueT{#2}{\textcolor{blue}{\textbf{A1 : }#2}}
    \IfValueT{#3}{\textcolor{ForestGreen}{\textbf{A2 : }#3}}
    \IfValueT{#4}{\textcolor{red!50!blue}{\textbf{A3 : }#4}}
    \IfValueT{#5}{\textcolor{Aquamarine}{\textbf{A4 : }#5}}
 }{}
}

% todo
\newcommand{\todo}[1]{
\ifthenelse{\draft=1}{\textcolor{red!50!blue}{\textbf{TODO : \textit{#1}}}}{}
}

\makeatletter
\makeatother

\usepackage{color}

@@

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{Raimbault and Bergeaud}

@@

\comment{(Juste) j'ai pas trop eu le temps de regarder la biblio mais c'est bizarre j'ai l'impression qu'il n'y a quasiment personne qui a fait ce qu'on veut faire, je dois mal chercher ? je mets ci-dessous de trucs reliés de prêt ou de loin, il faudra sûrement faire du tri !}

\cite{rietveld2001spatial} : impact of cross-border fuel differences and implications for gradual spatial taxing in the Netherlands

\cite{rietveld2005fuel} : statistical models to explain fuel price differences across European countries

\cite{macharis2010decision} : models the impact of spatial fuel price variation on patterns of inter-modality

\cite{gregg2009temporal} : spatial distribution of emissions, at the scale of the state (quite far from the subject)

\cite{combes2005transport} : determination of accurate transportation costs for France

% https://www.osti.gov/scitech/biblio/401732
% http://www.sciencedirect.com/science/article/pii/S0301421511002904

@@

\comment{(Juste) trouver un moyen de décrire la collecte des données sans dire qu'on l'a fait effectivement : architecture uniquement ?}

@@

\comment{(Juste) pointer vers le dataset produit par un Chinois (于思特) anonyme sur dataverse}

@@

\bibliographystyle{elsarticle-harv}
\bibliography{biblio}
%
